SPP-Perc: Peceptron Learning Based Enhanced Signature Path Prefetcher

### 2019-05-22 related.tex
minor

In addition to branch prediction~\cite{PerceptronPredictor},
perceptron-based learning has been applied to the area of cache
management.  Teran \textit{et al.} propose using perceptrons to
predict cache line resuse, bypass, and replacement~\cite{Perc_Reuse}.
Perceptron Learning trains weights selected by hashes of multiple
features, including the PC of the memory access instruction, some
other recent PCs, and two different shifts of the tag of the
referenced block. These features are used to index into weight tables,
and the weights are then thresholded to generate a prediction. When a
block from one of a few sampled sets~\cite{sdbp} is reused or evicted,
the corresponding weights are decremented or incremented, according to
the perceptron learning rule. Multiperspective Reuse
Prediction~\cite{Multiperspective} improves on Perceptron Learning by
contributing many new features. 
A similar work also proposed using perceptrons for filtering useless 
prefetches~\cite{ArxivPerc}. They implemented a basic Rosenblatt perceptron, using 
general error-correction learning. While they are able to reduce useless 
prefetches, they do not explore allowing the base-prefetcher to prefetch
unrestrained down the speculative path. Their design results in
increased accuracy but lowered cache coverage with low impact on
 overall performance.

@@

>>>>

@@

Wang and Lou propose a similar work where perceptrons filter useless
prefetches~\cite{ArxivPerc}.  In their design's primary focus was on
improving the accuracy of an unmodified baseline prefetcher.  Unlike
the scheme presented here, they implement a basic Rosenblatt
perceptron, with general error-correction learning.  While they are
able to increase accuracy, their design results in lower coverage, and
hence has low impact on overall performance.

In addition to branch prediction~\cite{PerceptronPredictor},
perceptron-based learning has been applied to the area of cache
management.  Teran \textit{et al.} propose using perceptrons to
predict cache line resuse, bypass, and replacement~\cite{Perc_Reuse}.
Perceptron Learning trains weights selected by hashes of multiple
features, including the PC of the memory access instruction, some
other recent PCs, and two different shifts of the tag of the
referenced block. These features are used to index into weight tables,
and the weights are then thresholded to generate a prediction. When a
block from one of a few sampled sets~\cite{sdbp} is reused or evicted,
the corresponding weights are decremented or incremented, according to
the perceptron learning rule. Multiperspective Reuse
Prediction~\cite{Multiperspective} improves on Perceptron Learning by
contributing many new features.
